The Concurrent Calculi Formalisation Benchmark

### 2023-10-11 paper/paper.tex
Fix a few typos.

Large scale mechanisation of concurrency theory is already possible,
\fxwarning{Citations?}
%(Paragraphs about related work in this vein)
and several papers in the realm of process calculi do include mechanised proofs
(e.g.~\cite{DBLP:conf/pldi/Castro-Perez0GY21,DBLP:conf/tacas/CastroFY20,lmcs:9985,
  DBLP:journals/jar/CruzFilipeMP23, Tirore:2023}), or
discuss proof mechanisation techniques
(e.g.~\cite{DBLP:journals/jar/BengtsonPW16, DBLP:conf/tphol/Gay01,
  DBLP:conf/ppdp/Thiemann19, DBLP:conf/forte/ZalakainD21}).  However, our
experience is that choosing the appropriate proof mechanisation techniques and
tools remains a significant challenge with few guidelines.  This often leads
researchers towards trial-and-error, attempting sub-optimal and ad-hoc
solutions; this increases the overall effort required by proof mechanisation,
and hampers the reuse of techniques and results.

@@

The three aspects we selected (linearity, scope extrusion, coinduction) are of
course not the only ones that may cause issues in mechanisations --- but they
are fundamental to the field of concurrency theory, and they emerge in most
mechanisations.  Moreover, the mechanisations of novel research results often
requires addressing more than just one of these aspects at once --- and we see
the combination of techniques as a next step beyond the scope of this challenge
(we discuss the topic in \cref{sec:going-beyond}).

>>>>

Large scale mechanisation of concurrency theory is already possible,
\fxwarning{Citations?}
%(Paragraphs about related work in this vein)
and several papers in the realm of process calculi do include mechanised proofs
(e.g.~\cite{DBLP:conf/pldi/Castro-Perez0GY21,DBLP:conf/tacas/CastroFY20,lmcs:9985,
  DBLP:journals/jar/CruzFilipeMP23, Tirore:2023}), or
discuss proof mechanisation techniques
(e.g.~\cite{DBLP:journals/jar/BengtsonPW16, DBLP:conf/tphol/Gay01,
  DBLP:conf/ppdp/Thiemann19, DBLP:conf/forte/ZalakainD21}).  However, our
experience is that choosing the appropriate proof mechanisation techniques and
tools remains a significant challenge with few guidelines.  This often leads
researchers towards trial-and-error, attempting sub-optimal and ad-hoc
solutions; this increases the overall effort required for proof mechanisation,
and hampers the reuse of techniques and results.

@@

The three aspects we selected (linearity, scope extrusion, coinduction) are of
course not the only ones that may cause issues in mechanisations --- but they
are fundamental to the field of concurrency theory, and they emerge in most
mechanisations.  Moreover, the mechanisation of novel research results often
requires addressing more than just one of these aspects at once --- and we see
the combination of techniques as a next step beyond the scope of this challenge
(we discuss the topic in \cref{sec:going-beyond}).
